\documentclass[11pt]{article}

% Packages
\usepackage[utf8]{inputenc}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{enumitem}
\usepackage{geometry}
\usepackage{fancyhdr}
\usepackage{mathtools}
\usepackage{multicol}
\usepackage[]{hyperref}

% Page layout
\geometry{margin=0.75in}
\pagestyle{fancy}
\fancyhf{}
\rhead{Ian Gallagher}
\lhead{Math 207C Homework}
\rfoot{\thepage}
\setlength{\headheight}{14pt}

% Commands
\newcommand{\vep}{\varepsilon}
\DeclarePairedDelimiter\abs{\lvert}{\rvert}

% Environments
\newtheoremstyle{problemstyle}
  {1em} % Space above
  {1em} % Space below
  {\normalfont} % Body font
  {} % Indent amount
  {\bfseries} % Theorem head font
  {} % Punctuation after theorem head
  {\newline} % Space after theorem head
  {} % Theorem head spec

\theoremstyle{problemstyle}
\newtheorem{problem}{Problem}

% Custom commands
\newenvironment{solution}
  {\noindent\textbf{Solution}\quad}
  {\hfill$\blacksquare$\par\vspace{1em}}

% Enumerate styles
\setlist[enumerate,1]{label=(\alph*), ref=\alph*}
% setlist[enumerate,2]{label=(\alph*), ref=\alph*}

% Title info
\title{Math 207C Homework \#\texttt{3}}
\author{Ian Gallagher}
\date{\today}

\begin{document}

\maketitle
\begin{enumerate}[label=(\arabic*)]
    \item Holmes \# 1.32(a)(b), 1.34(b), 1.35, 1.36, 1.38
    \item Holmes \# 2.1, 2.2(a)
\end{enumerate}


\begin{problem}[1.32]
Find a two-term asymptotic expansion, for small $\varepsilon$, of the solution
of the following problems:
  \begin{enumerate}
      \item $y'' + \varepsilon y' - y = 1$, where $y(0) = 0$ and $y(1) = 1$.
      \item $y'' + f(\varepsilon y) = 0$, where $y(0) = y(1) = 0$ and $f(s)$ is
        a smooth positive function.
  \end{enumerate}
\end{problem}


\begin{problem}[1.34]
This problem concerns aspects of the projectile problem.
  \begin{enumerate}
      \item Assuming $\tau_h \sim \tau_0 + \varepsilon \tau_1$, find $\tau_0$
        and $\tau_1$ from (1.46). Give a physical reason why $\tau_1$ is
        positive.
      \item Find a two-term expansion for the time at which the projectile
        reaches its maximum height. How much higher does the projectile get in
        the nonuniform gravitational field? (You should find a first-term
        approximation for this.)
  \end{enumerate}
\end{problem}

\begin{problem}[1.35]
In the projectile problem, to account for air resistance, one obtains the
equation
\[
\frac{d^2x}{dt^2} = -\frac{gR^2}{(x + R)^2} - \frac{k}{R + x} \frac{dx}{dt},
\]
where $k$ is a nonnegative constant. Assume here that $x(0) = 0$ and $x'(0) =
v_0$.
  \begin{enumerate}
      \item What is the nondimensional version of this problem if one uses the
        same scaling as in Sect.~1.1?
      \item Find a two-term asymptotic expansion of the solution for small
        $\varepsilon$. Assume in doing this that $\alpha = kv_0/(gR)$ is
        independent of $\varepsilon$.
      \item Does the addition of air resistance increase or decrease the flight
        time?
  \end{enumerate}
\end{problem}

\begin{problem}[1.36]
The eigenvalue problem for the vertical displacement, $y(x)$, of an elastic
string with variable density is
\[
y'' + \lambda^2 \rho(x, \varepsilon) y = 0, \quad \text{for } 0 < x < 1,
\]
where $y(0) = y(1) = 0$. For small $\varepsilon$ assume $\rho \sim 1 +
\varepsilon \mu(x)$, where $\mu(x)$ is positive and continuous. In this case the
solution $y(x)$ and eigenvalue $\lambda$ depend on $\varepsilon$, and the
appropriate expansions are
\[
  y \sim y_0(x) + \varepsilon y_1(x) \quad \text{and} \quad \lambda \sim
  \lambda_0 + \varepsilon \lambda_1
\]
(better expansions will be discussed in Sect.~3.6).
  \begin{enumerate}
      \item Find $y_0$ and $\lambda_0$.
      \item Find $y_1$ and $\lambda_1$.
  \end{enumerate}
\end{problem}

\begin{problem}[1.38]
The equation for the displacement, $u(x)$, of a weakly nonlinear string, on an
elastic foundation and with a uniform forcing, is
\[
  \frac{d}{dx} \left( \frac{u_x}{\sqrt{1 + \varepsilon (u_x)^2}} \right) - k^2 u
  = 1, \quad \text{for } 0 < x < 1,
\]
where $u(0) = u(1) = 0$ and $k$ is a positive constant. Find a two-term
expansion of the solution for small $\varepsilon$. You should find, but do not
need to solve, the problem for the second term.
\end{problem}

\begin{problem}[2.1]
The Friedrichs model problem for a boundary layer in a viscous fluid is 
(Friedrichs, 1941)
\[
\varepsilon y'' = a - y', \quad \text{for } 0 < x < 1,
\]
where $y(0) = 0$, $y(1) = 1$, and $a$ is a given positive constant with $a \ne 1$.
  \begin{enumerate}
      \item After finding the first term of the inner and outer expansions,
        derive a composite expansion of the solution of this problem.
      \item Derive a two-term composite expansion of the solution of this
        problem.
  \end{enumerate}
\end{problem}

\begin{problem}[2.2]
Find a composite expansion of the solution of the following problems:
  \begin{enumerate}
      \item $\varepsilon y'' + 2y' + y^3 = 0$ for $0 < x < 1$, where $y(0) = 0$
        and $y(1) = \tfrac{1}{2}$.
  \end{enumerate}
\end{problem}

\end{document}

